Automatically generated NE tagged corpora for English and Hungarian

### 2012-03-25 paper/engNERwiki.tex
My nice paragraph, bruhuhu...

As of version 3.7, the DBpedia ontology allows multiple superclasses, making the hierarchy a directed acyclic graph\footnote{http://blog.dbpedia.org/2011/09/11/dbpedia-37-released-including-15-localized-editions}. This introduces the problem of selecting the right superclass, and hence, CoNLL mapping for classes with more than one parent. In version 3.7, the only such class is \textit{Library}, which can be traced back to both \textit{Place} and \textit{Organisation}. Hence, we picked the right NE mapping manually, and added it to the mapping file.

%DBpedia guidelines suggest that only the first parent is retained. Unfortunately, this approach already fails to assign the correct CoNLL NE tag to our only example. The reason behind this failure is that multiple parents in an ontology show an inherent ambiguity in the class in question: it is entirely natural to think of a library as a location as well as a public organization. DBpedia's guidelines prefer \texttt{Organisation}; CoNLL's prefer LOCATION. Hence, we picked the right NE mapping manually and added it to the mapping file.

>>>>

As of version 3.7, the DBpedia ontology allows multiple superclasses, making the hierarchy a directed acyclic graph\footnote{http://blog.dbpedia.org/2011/09/11/dbpedia-37-released-including-15-localized-editions}. Since selecting the right superclass, and hence, CoNLL tag for classes with more than one parent cannot be reliably done automatically, the class-to-category mapping has to be determined manually. In version 3.7, the only such class is \textit{Library}, which can be traced back to both \textit{Place} and \textit{Organisation}.
